### 2019-05-10 README.Rmd
added reviewer responses and update package loading
added binder

[![Paper](https://img.shields.io/badge/Paper-10.1101/366476-lightgrey.svg)](https://doi.org/10.1101/366476)
[![DOI](https://zenodo.org/badge/127124135.svg)](https://zenodo.org/badge/latestdoi/127124135)

@@

- Install the required packages using the following script. Versioned to "2018-06-19".

@@

This analysis can be run in a docker container based on the tidyverse docker image. To run the docker image run:

>>>>

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/ExploreBCGOnOutcomes/master?urlpath=rstudio)
[![Paper](https://img.shields.io/badge/Paper-10.1101/366476-lightgrey.svg)](https://doi.org/10.1101/366476)
[![DOI](https://zenodo.org/badge/127124135.svg)](https://zenodo.org/badge/latestdoi/127124135)

@@

- Install the required packages using the following script. Versioned to "2018-06-19" using the `checkpoint` package.

@@

To ensure full reproducibility, this analysis can be run in a docker container based on the tidyverse docker image. To run the docker image run:
